Supplementary material for: non-coding RNAs of bird genomes

### 2014-05-20 paper/manuscript.tex
Added accessions and a tree to the Sup. Mat.

Many of the lncRNAs have been associated with cancer, sparking a minor
review industry \cite{Prensner:2011,Spizzo:2012}. Three examples of
these that are also conserved in the birds are described below.

@@

Magnus Alm Rosenblad (Univ. of Gothenburg) and Eric Nawrocki (HHMI
Janelia Farm) for useful discussions.

>>>>

The majority ($>80\%$) of genome-wide association studies of cancer
identify loci outside of protein-coding genes
\cite{Cheetham:2013}. Many of these are loci are now known to be
transcribed into lncRNAs. Furthermore, many lncRNAs are differentially
expressed in tumorous tissues \cite{Chan:2002}, suggesting further
mechanistic links with the aberrant gene expression associated cancer
progression. In our work we have identified three examples of these
that are also conserved in the birds are described below.

@@

Magnus Alm Rosenblad (Univ. of Gothenburg) and Eric Nawrocki (HHMI
Janelia Farm) for useful discussions. Matthew Walters for assistance
with figures.

### 2014-05-20 paper/supplementary-material.tex
Added accessions and a tree to the Sup. Mat.

 \begin{figure}[ht]
   \includegraphics[width=0.5\textwidth]{figures/figure2.pdf}
\caption{Additional homologs of some sparsely represented RNA families were
discovered using dedicated search strategies combined with highly
sensitive settings, synteny information, lineage-specific CMs and
subsequent manual inspection.}\label{fig:2}
 \end{figure}

@@

>>>>

 \begin{figure}[ht]
   \includegraphics[width=0.75\textwidth]{figures/figure2.pdf}
\caption{Additional homologs of some sparsely represented RNA families were
discovered using dedicated search strategies combined with highly
sensitive settings, synteny information, lineage-specific CMs and
subsequent manual inspection.}\label{fig:2}
 \end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.9\textwidth]{figures/phylo-tree.pdf}
  \caption[]{The phylogenetic relationships between the Avian species
    used in this study. This figure has been reproduced, with permission from \cite{birds:14a}.}\label{fig:15}
\end{figure}

\subsection*{Database accessions}

The NCBI BioProject/SRA and Study IDs for the genomes used in this study
are are listed below.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|l|l|l|}
    \hline
Species & BioProject ID & SRA ID & Study ID \\
    \hline
\emph{Chaetura pelagica} & PRJNA210808  & SRA092327 & SRP026688\\
\emph{Calypte anna} & PRJNA212866 & SRA096094 & SRP028275\\
\emph{Charadrius vociferus} & PRJNA212867 & SRA096158 & SRP028286\\
\emph{Corvus brachyrhynchos} & PRJNA212869 & SRA096200 & SRP028317\\
\emph{Cuculus canorus} & PRJNA212870 & SRA096365 & SRP028349\\
\emph{Manacus vitellinus} & PRJNA212872 & SRA096507 & SRP028393\\
\emph{Ophisthocomus hoazin} & PRJNA212873 & SRA096539 & SRP028409\\
\emph{Picoides pubescens} & PRJNA212874 & SRA097131 & SRP028625\\
\emph{Struthio camelus} & PRJNA212875 & SRA097407 & SRP028745\\
\emph{Tinamus guttatus} & PRJNA212876 & SRA097796 & SRP028753\\
\emph{Acanthisitta chloris} & PRJNA212877 & SRA097960 & SRP028832\\
\emph{Apaloderma vittatum} & PRJNA212878 & SRA097967 & SRP028834\\
\emph{Balearica regulorum} & PRJNA212879 & SRA097970 & SRP028839\\
\emph{Buceros rhinoceros} & PRJNA212887 & SRA097991 & SRP028845\\
\emph{Antrostomus carolinensis} & PRJNA212888 & SRA098079 & SRP028883\\
\emph{Cariama cristata} & PRJNA212889 & SRA098089 & SRP028884\\
\emph{Cathartes aura} & PRJNA212890 & SRA098145 & SRP028913\\
\emph{Chlamydotis macqueenii} & PRJNA212891 & SRA098203 & SRP028950\\
\emph{Colius striatus} & PRJNA212892 & SRA098342 & SRP028965\\
\emph{Eurypyga helias} & PRJNA212893 & SRA098749 & SRP029147\\
\emph{Fulmarus glacialis} & PRJNA212894 & SRA098806 & SRP029180\\
\emph{Gavia stellata} & PRJNA212895 & SRA098829 & SRP029187\\
\emph{Haliaeetus albicilla} & PRJNA212896 & SRA098868 & SRP029203\\
\emph{Haliaeetus leucocephalus} & PRJNA237821 & SRX475899 & SRP038924\\
                         & SRX475900   &           &          \\
                         & SRX475901   &           &          \\
                         & SRX475902   &           &          \\
\emph{Leptosomus discolor} & PRJNA212897 & SRA098894 & SRP029206\\
\emph{Merops nubicus} & PRJNA212898 & SRA099305 & SRP029278\\
\emph{Mesitornis unicolor} & PRJNA212899 & SRA099409 & SRP029309\\
\emph{Nestor notabilis} & PRJNA212900 & SRA099410 & SRP029311\\
\emph{Pelecanus crispus} & PRJNA212901 & SRA099411 & SRP029331\\
\emph{Phaethon lepturus} & PRJNA212902 & SRA099412 & SRP029342\\
\emph{Phalacrocorax carbo} & PRJNA212903 & SRA099413 & SRP029344\\
\emph{Phoenicopterus ruber} & PRJNA212904 & SRA099414 & SRP029345\\
\emph{Podiceps cristatus} & PRJNA212905 & SRA099415 & SRP029346\\
\emph{Pterocles gutturalis} & PRJNA212906 & SRA099416 & SRP029347\\
\emph{Tauraco erythrolophus} & PRJNA212908 & SRA099418 & SRP029348\\
\emph{Tyto alba} & PRJNA212909 & SRA099419 & SRP029349\\
\emph{Nipponia nippon} & PRJNA232572 & SRA122361 & SRP035852\\
\emph{Egretta garzetta} & PRJNA232959 & SRA123137 & SRP035853\\
\hline
    \end{tabular}
  \end{center}
  \caption{The NCBI BioProject/SRA and Study IDs used in this study. }
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|l|l|l|}
    \hline
Species & BioProject ID & SRA ID & Study ID \\
    \hline
\multicolumn{4}{|l|}{Genomes released before}\\
\hline
\emph{Aptenodytes forsteri} & PRJNA235982 & SRA129317 & SRP035855\\
\emph{Pygoscelis adeliae} & PRJNA235983 & SRA129318 & SRP035856\\
\emph{Gallus gallus} & PRJNA13342 & SRA030184 & SRP005856\\
\emph{Taeniopygia guttata} & PRJNA17289 & SRA010067 & SRP001389\\
\emph{Meleagris gallopavo} & PRJNA42129 & Unknown & Unknown\\
\emph{Melopsittacus undulatus} & PRJEB1588 & ERA200248 & ERP002324\\
\emph{Anas platyrhynchos} & PRJNA46621 & SRA010308 & SRP001571\\
\emph{Columba livia} & PRJNA167554 & SRA054954 & SRP013894\\
\emph{Falco peregrinus} & PRJNA159791 & SRA055082 & SRP013939\\
\emph{Geospiza fortis} & PRJNA156703 & SRA051234 & SRP011940\\
\hline
\multicolumn{4}{|l|}{Outgroups}\\
\hline
\emph{Homo sapiens} & & & \\
\emph{Alligator mississippiensis} & & & \\
\emph{Chelonia mydas} & & & \\
\hline
\multicolumn{4}{|l|}{RNA-seq data}\\
\hline
\emph{Gallus gallus} & PRJNA204941 & NA & NA \\
\emph{Gallus gallus} & NA & & SRP041863 \\
\hline
    \end{tabular}
  \end{center}
  \caption{The NCBI BioProject/SRA and Study IDs for the previously
    published genomes used in this study.}
\end{table}
